EDLD 651 Final Project Presentation

### 2020-11-27 presentation.Rmd
update presentation

# Dwelling on Complexity with Dynamic Fractals
*How much time will participants spend looking at dynamic fractals as they increase or decrease in complexity?*
<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mandy4.png" height="360" width="480">

@@

## Victories and things to celebrate
- making GIFs
- super neat plots
- research question was answered
- hypothesis was correct

>>>>

# Dwelling on Complexity with Dynamic Fractals

*How much time will participants spend looking at dynamic fractals as they increase or decrease in complexity?*

<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mandy4.png" height="360" width="480">

@@

## Victories and things to celebrate
- making GIFs
- super neat plots
- research question was answered
- hypothesis was correct
- using R to make this presentation
